Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

Particles released in \textit{Papa\_winter} are thus exported faster and in greater numbers than expected from gravitational sinking. Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time. Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.

>>>>

Particles released in \textit{Papa\_winter} are thus exported faster and in greater numbers than expected from gravitational sinking. Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time.

\fixme{Here Fig6b should be included an described. The key points are (1) the large difference between velocity class that have $w_s\ll w_{adv}$, and the one that have $w_s\sim w_{adv}$, (2) despite the large difference in \% of particles exported the biomass fluxes are of the same order of magnitude when $\xi=4$ as it is often reported in the ocean, and (3) the predictible decrease in biomass export flux when changing the slope based on equation (8). }

\begin{equation}
    \frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
\end{equation}

Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.
